The yaq Project: \\ Standardized Software Enabling Flexible Instrumentation

### 2022-11-11 paper.tex
captions

\begin{figure}
	\includegraphics[width=\columnwidth]{figures/network}
\caption{\label{fig:network} Networking diagram}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figures/client_spectrum}
	\caption{  \label{fig:foundation} \yaq{} scales from simple scripts to integrations with featureful frameworks.}
\end{figure}

>>>>

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/network}
    \caption{\label{fig:network} Simplified network diagram for a hypothetical instrument. Three computers are connected via orange Ethernet cables and a network switch (middle right). Some of the computers are also connected to hardware peripherals via one of six interfaces (colored lines). For each interface, the computer runs a \yaq{} daemon (small colored squares). The top and bottom computers are also running \yaq{} client applications.}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figures/client_spectrum}
  \caption{\label{fig:foundation} Representations of three very different \yaq{} client experiences. Top: light-weight scripting. Middle: graphical user interface. Bottom: integration with Bluesky for data collection. In all three cases the same daemons are addressed.}
\end{figure}
